Article Title

### 2014-01-28 plos.tex
corrected the captions in the supplementary figures.

We sought statistically efficient estimators of neural correlation matrices in recordings from large, dense groups of cortical neurons.  Using fast 3D random-access laser scanning microscopy of calcium signals, we recorded the activity of nearly every neuron in volumes 200 $\mu$m wide and 100 $\mu$m deep (150--350 cells) in mouse visual cortex.  We hypothesized that in these dense recordings, the correlation matrix should be best represented as the combination of a sparse matrix of pairwise partial correlations representing local interactions and a low-rank component representing common fluctuations and external inputs.  Indeed, in cross-validation tests, the covariance matrix estimator with this structure consistently outperformed other regularized estimators. The sparse component of the estimate expressed a graph of interactions organized with respect to the physical distances and orientation tuning properties of cells: The density of positive \sq{excitatory} connections decreased rapidly with geometric distances and with differences in orientation preference whereas the negative \sq{inhibitory} connections were less selective.  Because of its superior performance, this ``sparse + latent'' estimator likely provides a more physiologically relevant representation of the functional connectivity in dense recordings than the sample correlation matrix.

@@

Neural correlations do not come with ready or unambiguous mechanistic interpretations. They can arise from monosynaptic or polysynaptic interactions, common or correlated inputs, oscillations, top-down modulation, and background network fluctuations, or a combination of these and other mechanisms \cite{Perkel:1967, Moore:1970, Shadlen:1998, Salinas:2001, Ostojic:2009, Rosenbaum:2011}. But multineuronal recordings do provide more information than an equivalent number of separately recorded pairs of cells. For example, the eigenvalue decomposition of the covariance matrix expresses shared correlated activity components across the population; common fluctuations of population activity may be accurately represented by only a few eigenvectors that affect all correlation coefficients. On the other hand, a correlation matrix can be specified using the \emph{partial correlations} between pairs of the recorded neurons. The partial correlation coefficient between two neurons reflects their linear association conditioned on the activity of all the other recorded cells.  As such, partial correlations more closely reflect the direct causal effects between components of complex systems than correlations; partial correlations have been used to describe interactions between genes in functional genomics \cite{Schafer:2005, Peng:2009} and between brain regions in imaging studies \cite{Varoquaux:2012, Ryali:2012}. These opportunities have not yet been explored in neurophysiological studies, as most studies have only considered the distributions of pairwise correlations \cite{Zohary:1994, Bair:2001, Smith:2008, Ecker:2010}.

@@

Estimation can be improved through \emph{regularization},  the technique of deliberately imposing a structure on an estimate in order to reduce its estimation error \cite{Schafer:2005, Bickel:2006}. To \sq{impose a structure} on an estimate means to bias (\sq{shrink}) it toward a reduced representation  with fewer free parameters, which is often referred to as the \emph{target estimate}.   The optimal target estimate and the optimal amount of shrinkage can be obtained from the data sample either analytically \cite{Ledoit:2003, Ledoit:2004, Schafer:2005},  or by cross-validation \cite{Friedman:1989}. An estimator that produces estimates that are, on average, closer to the truth for a given sample size is said to be more \emph{efficient} than other estimators.

@@

The necessity and benefits of regularization increase with the size of the recorded population. With the advent of  big neural data, the search for optimal regularization schemes will become increasingly relevant in any model of population activity. Since optimal regularization schemes are specific to systems under investigation, the inference of functional connectivity in large scale neural data will entail the search for optimal regularization schemes that may involve combinations of heuristic rules and numerical techniques specially designed for each neural circuit.

@@

To address these questions, we evaluated four regularized covariance matrix estimators that imposed different structures on the estimate. The estimators are designated as follows:
\begin{description}
\item[$C_{\sf 0}$] -- sample covariance matrix, the unbiased, unregularized estimator.
\item[$C_{\sf diag}$] -- linear shrinkage of correlations toward zero.
\item[$C_{\sf factor}$] -- linear shrinkage of the covariances toward a low-rank matrix, representing inputs from unobserved factors (latent units).
\item[$C_{\sf sparse}$] -- sparse partial correlations, \ie a large fraction of the \emph{partial} correlations between pairs of neurons are set to zero.
\item[$C_{\sf sparse+latent}$] -- sparse partial correlations between the recorded neurons \emph{and} linear interactions with a number of latent units.
\end{description}

@@

We then performed a cross-validated evaluation to establish which of the four regularized estimators was most efficient for the population activity of dense groups of neurons in mouse primary visual cortex recorded with high-speed 3D random-access two-photon imaging of calcium signals. In our data, the sample correlation coefficients were largely positive and low.  We found that the best estimate of the correlation matrix was $C_{\sf sparse+latent}$.  This estimator revealed a sparse network of partial correlations, which we call \sq{interactions} here, between the observed neurons and inferred several latent units exerting linear effects on the observed neurons. We analyzed these networks of partial correlations and found the following: Whereas noise correlations were predominantly positive, the inferred interactions had a large fraction of negative values possibly reflecting inhibitory circuitry.  Moreover, we found that these interactions exhibited a stronger relationship on the physical distances and differences in preferred orientations than noise correlations. In contrast, the inferred negative interactions were less selective.

\section*{Results}
% Results and Discussion can be combined.
\paragraph{Covariance estimation}
The covariance matrix is defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; the $p\times 1$ vector $x$ is a single observation of the firing rates of $p$ neurons over time $\Delta t$; and $\mu$ is the vector of expected firing rates.  The usual way to estimate the covariance matrix is to calculate the \emph{sample covariance matrix} $C_{\sf 0}$ from the empirical sample of observations $x(t),\; t=1,\ldots,n$ as
\begin{equation}\label{eq:sample}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom in one neuron's activity within the sample ($\nu=n-1$ if observations are independent). For noise correlations, the true mean $\mu$ and the sample mean $\bar x$ are conditioned on the stimulus. In this study, we estimate the true mean, $\mu$, using the sample mean $\bar x$, but seek a better estimate of the covariance matrix than the sample correlation matrix, $C_{\sf 0}$.

Given an arbitrary covariance matrix estimate $C$, the corresponding correlation matrix $R$ is calculated by normalizing $C$ by its diagonal (variance estimates):
\begin{equation}\label{eq:precision}
    R = \left(I\circ C\right)^{-\frac 1 2} C \left(I\circ C\right)^{-\frac 1 2},
\end{equation}
where $\circ$ denotes entrywise matrix product (Hadamard product) and $I$ is the $p\times p$ identity matrix. 
Similarly, the matrix of partial correlations $P$ is computed by normalizing the \emph{precision matrix} $C^{-1}$:
\begin{equation}\label{eq:partial}
    P = -\left(I\circ C^{-1}\right)^{-\frac 1 2} C^{-1} \left(I\circ C^{-1}\right)^{-\frac 1 2}
\end{equation}

@@

\begin{FPfigure}
    \begin{center}
        \includegraphics{./figures/Figure02.pdf}
    \end{center}
    \caption{{\bf Regularized estimators whose structure matches the true structure in the data are more efficient.}
        {\bf Row 1.} Graphical representations of the target estimates of the four respective regularized covariance matrix estimators.  Recorded neurons are represented by green spheres and latent units by light-shaded spheres.  Edges represent non-zero partial correlations.
        {\bf Row 1, A}.  For estimator $C_{\sf diag}$, the target estimate is a diagonal matrix, which describes systems that lack linear associations. 
        {\bf  Row 1, B.} For estimator $C_{\sf factor}$, the target estimate is a factor model (low-rank matrix plus a diagonal matrix), representing systems in which correlations arise due to common input from latent units. 
        {\bf  Row 1, C}. For estimator $C_{\sf sparse}$, the covariance matrix is approximated as the inverse of a sparse matrix. This approximation describes systems in which correlations arise from a sparse set of  linear associations between the observed units. 
        {\bf  Row 1, D}.  For estimator $C_{\sf sparse+latent}$, the covariance matrix is approximated as the inverse of the sum of a sparse matrix and a low-rank matrix. This approximation describes a model wherein correlations arise due to sparse associations between the recorded cells \emph{and} with several latent units. \\
{\bf Row 2:} Examples of $50\times 50$ correlation matrices corresponding to each structure: {\bf A.} the diagonal correlation matrix, {\bf B.} a factor model with two latent units, {\bf C.}  a correlation matrix with 85\%  off-diagonal zeros, and {\bf  D.} a correlation matrix whose inverse is the sum of a rank-1 (\ie one latent unit) matrix and a sparse matrix with 89\% off-diagonal zeros. 
\\
{\bf Row 3:} Sample correlation matrices calculated from samples of size $n=1000$ drawn from simulated random processes with respective correlation matrices from row 2.  The structure of the sample correlation matrix is difficult to discern.
\\
{\bf Row 4:} Correlation matrix estimates computed by estimators with matching structure from the same data as the sample correlation matrices in Row 3. The regularized estimates are closer to the truth than the sample correlation matrices.
\\
{\bf Row 5:} Excess losses (Eq.~\ref{eq:excess-loss}) for the five estimators as a function of sample size. The error bars indicate the standard error of the mean based on 30 samples.  Estimators with structure that matches the model used to generate the data converged to zero faster than the other estimators. Some exceptions occur when the sample is too small to reveal the structure in the data. In these cases estimators with simpler structures can be more efficient.
\\
{\bf Row 6:} Relative cross-validation losses (Eq.~\ref{eq:rel-cv-loss}) for the five estimators with respect to the matching estimator. Error bars indicate the standard error of the mean based on 30 samples.
    }
    \label{fig:02}
\end{FPfigure}

@@

The target of estimator $C_{\sf factor}$ is the factor model $L + \Psi$, where $L$ is the $p\times p$ positive definite matrix with low rank and $\Psi$ is the diagonal matrix of independent variances.  The estimator, 
\begin{equation}\label{eq:c-factor}
C_{\sf factor} = (1-\lambda) C_{\sf 0} + \lambda (L + \Psi),
\end{equation}
has two hyperparameters: the rank of $L$ (\ie the number of latent factors) and the shrinkage intensity $\lambda$. The structure imposed by $C_{\sf factor}$ favors conditions in which the population activity is linearly driven by a number of latent factors that affect many cells while direct interactions between cells are insignificant (\figref{02}{Row 1, B}).

Estimator $C_{\sf sparse}$ is produced by approximating the sample covariance matrix whose inverse is sparse: 
\begin{equation}\label{eq:c-sparse}
C_{\sf sparse} = S^{-1}.
\end{equation}
Here $S$ is a sparse matrix, \ie one in which a large fraction of off-diagonal elements are set to zero.  The estimator has one hyperparameter that determines the sparsity (fraction of off-diagonal zeros) in $S$. The problem of finding the optimal set of non-zero elements of the precision matrix is known as \emph{covariance selection} \cite{Dempster:1972}. The structure imposed by $C_{\sf sparse}$ favors conditions in which neural correlations arise from direct linear effects (\sq{interactions}) between some pairs of neurons (\figref{02}{Row 1, C}).  We will sometimes refer to sparse partial correlations between neurons simply  as \sq{interactions}.

@@

@@

The evaluation of a covariance matrix estimator, $C,$ is performed with respect to a \emph{loss function} $\loss{C,\Sigma}$ to quantify the discrepancy between the estimate and the truth, $\Sigma$.  The loss function must attain its minimum when $C=\Sigma$.

@@

The choice of normal loss function is motivated by mathematical convenience. We expect that the main conclusions of our study will not change qualitatively with other well behaved loss functions, such as Stein's entropy loss or quadratic loss \cite{James:1961, Fan:2008, Ledoit:2004, Schafer:2005}.

@@

We drew 30 independent samples of size $n=250$, 500, 1000, 2000, and 4000 from model and computed the excess loss for each of the five estimators.  The hyperparameters of the regularized estimators were optimized by nested cross-validation using only the data in the sample.  All the regularized estimators produced better estimates (lower excess loss) than the sample covariance matrix.  However, estimators whose structure matched the true model typically outperformed the other estimators (\figref{02}{\,row 5}).  There were two exceptions: First, for some smaller samples, the data were insufficient to reveal the true correlation structure and the estimators with simpler structures, $C_{\sf diag}$ and $C_{\sf factor}$, often outperformed the estimators with the matching structure (\figref{02}{\,Row 5, C and D}).  Second, $C_{\sf sparse+latent}$ often performed as well as $C_{\sf sparse}$ on data from models without latent units because.  However, in theses cases it reliably inferred the correct number of latent units which was zero.

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./figures/Figure-Supp01.pdf}
\end{center}
\caption{{\bf All-to-all performance comparisons of the sample covariance matrix and the four regularized estimators with respect to multivariate normal cross-validation loss.}
}
\label{supp:01}
\end{figure}

\begin{figure}[!ht]
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=8.3cm}}]{figure}[\FBwidth]
{\caption{{\bf The sparse+latent estimator outperforms the other estimators under the quadratic loss (Eq.~\ref{eq:quadratic}) just as it did under the normal loss (Eq.~\ref{eq:loss}) used in Fig.~\ref{fig:04}}.
}
\label{supp:02}}
{\includegraphics{./figures/Figure-Supp02.pdf}}
\end{figure}

>>>>

We sought statistically efficient estimators of neural correlation matrices in recordings from large, dense groups of cortical neurons.  Using fast 3D random-access laser scanning microscopy of calcium signals, we recorded the activity of nearly every neuron in volumes 200 $\mu$m wide and 100 $\mu$m deep (150--350 cells) in mouse visual cortex.  We hypothesized that in these dense recordings, the correlation matrix should be best represented as the combination of a sparse matrix of pairwise partial correlations representing local interactions and a low-rank component representing common fluctuations and external inputs.  Indeed, in cross-validation tests, the covariance matrix estimator with this structure consistently outperformed other regularized estimators. The sparse component of the estimate expressed a graph of interactions organized with respect to the physical distances and orientation tuning properties of cells: The density of positive \sq{excitatory} interactions decreased rapidly with geometric distances and with differences in orientation preference whereas the negative \sq{inhibitory} interactions were less selective.  Because of its superior performance, this ``sparse + latent'' estimator likely provides a more physiologically relevant representation of the functional connectivity in dense recordings than the sample correlation matrix.

@@

Neural correlations do not come with ready or unambiguous mechanistic interpretations. They can arise from monosynaptic or polysynaptic interactions, common or correlated inputs, oscillations, top-down modulation, and background network fluctuations, and other mechanisms \cite{Perkel:1967, Moore:1970, Shadlen:1998, Salinas:2001, Ostojic:2009, Rosenbaum:2011}. But multineuronal recordings do provide more information than an equivalent number of separately recorded pairs of cells. For example, the eigenvalue decomposition of the covariance matrix expresses shared correlated activity components across the population; common fluctuations of population activity may be accurately represented by only a few eigenvectors that affect all correlation coefficients. On the other hand, a correlation matrix can be specified using the \emph{partial correlations} between pairs of the recorded neurons. The partial correlation coefficient between two neurons reflects their linear association conditioned on the activity of all the other recorded cells.  When a large fraction of the interacting variables are observed, partial correlations more closely reflect the direct causal effects between components of complex systems than correlations. Partial correlations have been used to describe interactions between genes in functional genomics \cite{Schafer:2005, Peng:2009} and between brain regions in imaging studies \cite{Varoquaux:2012, Ryali:2012}. These opportunities have not yet been explored in neurophysiological studies, as most studies have only considered the distributions of pairwise correlations \cite{Zohary:1994, Bair:2001, Smith:2008, Ecker:2010}.

@@

Estimation can be improved through \emph{regularization},  the technique of deliberately imposing a structure on an estimate in order to reduce its estimation error \cite{Schafer:2005, Bickel:2006}. To \sq{impose a structure} on an estimate means to bias (\sq{shrink}) it toward a reduced representation  with fewer free parameters, the \emph{target estimate}.   The optimal target estimate and the optimal amount of shrinkage can be obtained from the data sample either analytically \cite{Ledoit:2003, Ledoit:2004, Schafer:2005}  or by cross-validation \cite{Friedman:1989}. An estimator that produces estimates that are, on average, closer to the truth for a given sample size is said to be more \emph{efficient} than other estimators.

@@

The necessity and benefits of regularization increase with the size of the recorded population. With the advent of  big neural data \cite{Alivasatos:2013}, the search for optimal regularization schemes will become increasingly relevant in any model of population activity. Since optimal regularization schemes are specific to systems under investigation, the inference of functional connectivity in large scale neural data will entail the search for optimal regularization schemes that may involve combinations of heuristic rules and numerical techniques specially designed for each neural circuit.

@@

To address these questions, we evaluated four regularized covariance matrix estimators that imposed different structures on the estimate. The estimators are designated as follows:
\begin{description}
\item[$C_{\sf 0}$] -- sample covariance matrix, the unbiased, unregularized estimator.
\item[$C_{\sf diag}$] -- linear shrinkage of covariances toward zero, \ie toward a diagonal covariance matrix.
\item[$C_{\sf factor}$] -- linear shrinkage of the covariances toward a low-rank matrix, representing inputs from unobserved factors (latent units).
\item[$C_{\sf sparse}$] -- sparse partial correlations, \ie a large fraction of the \emph{partial} correlations between pairs of neurons are set to zero.
\item[$C_{\sf sparse+latent}$] -- sparse partial correlations between the recorded neurons \emph{and} linear interactions with a number of latent units.
\end{description}

@@

We then performed a cross-validated evaluation to establish which of the four regularized estimators was most efficient for the population activity of dense groups of neurons in mouse primary visual cortex recorded with high-speed 3D random-access two-photon imaging of calcium signals. In our data, the sample correlation coefficients were largely positive and low.  We found that the best estimate of the correlation matrix was $C_{\sf sparse+latent}$.  This estimator revealed a sparse network of partial correlations, which we call \sq{interactions} here, between the observed neurons; it also inferred several latent units exerting linear effects on the observed neurons. We analyzed these networks of partial correlations and found the following: Whereas noise correlations were predominantly positive, the inferred interactions had a large fraction of negative values possibly reflecting inhibitory circuitry.  Moreover, we found that these interactions exhibited a stronger relationship to the physical distances and to the differences in preferred orientations than noise correlations. In contrast, the inferred negative interactions were less selective.

\section*{Results}
% Results and Discussion can be combined.
\paragraph{Covariance estimation}
The covariance matrix is defined as
\begin{equation}\label{eq:true-covariance}
    \Sigma = \E{(x-\mu)(x-\mu)^\T},\quad \mu = \E{x}
\end{equation}
where $\E{\cdot}$ denotes expectation; the $p\times 1$ vector $x$ is a single observation of the firing rates of $p$ neurons over time $\Delta t$; and $\mu$ is the vector of expected firing rates.  The usual way to estimate the covariance matrix is to calculate the \emph{sample covariance matrix} $C_{\sf 0}$ from the empirical sample of observations $x(t),\; t=1,\ldots,n$ as
\begin{equation}\label{eq:sample}
    C_{\sf 0} = \frac 1 \nu \sum\limits_{t=1}^n (x(t)-\bar x)(x(t)-\bar x)^\T,\quad \bar x= \frac 1 n \sum\limits_{t=1}^n x(t)
\end{equation}
where $\nu$ is the number of degrees of freedom in one neuron's activity within the sample ($\nu=n-1$ if observations are independent). For noise correlations, the true mean $\mu$ and the sample mean $\bar x$ are conditioned on the stimulus. In this study, we estimate the true mean, $\mu$, using the sample mean, $\bar x$, but seek a better estimate of the covariance matrix than the sample correlation matrix, $C_{\sf 0}$.

Given an arbitrary covariance matrix estimate $C$, the corresponding correlation matrix $R$ is calculated by normalizing $C$ by its diagonal (variance estimates):
\begin{equation}\label{eq:precision}
    R = \left(I\circ C\right)^{-\frac 1 2} C \left(I\circ C\right)^{-\frac 1 2},
\end{equation}
where $\circ$ denotes the entrywise matrix product (Hadamard product) and $I$ is the $p\times p$ identity matrix. 
Similarly, the matrix of partial correlations $P$ is computed by normalizing the \emph{precision matrix} $C^{-1}$:
\begin{equation}\label{eq:partial}
    P = -\left(I\circ C^{-1}\right)^{-\frac 1 2} C^{-1} \left(I\circ C^{-1}\right)^{-\frac 1 2}
\end{equation}

@@

\begin{FPfigure}
    \begin{center}
        \includegraphics{./figures/Figure02.pdf}
    \end{center}
    \caption{{\bf Regularized estimators whose structure matches the true structure in the data are more efficient.}
    {\bf Row 1.} Graphical representations of the target estimates of the four respective regularized covariance matrix estimators.  Recorded neurons are represented by green spheres and latent units by light-shaded spheres.  Edges represent non-zero partial correlations, \ie \sq{interactions}.
        {\bf Row 1, A}.  For estimator $C_{\sf diag}$, the target estimate is a diagonal matrix, which describes systems that lack linear dependencies. 
        {\bf  Row 1, B.} For estimator $C_{\sf factor}$, the target estimate is a factor model (low-rank matrix plus a diagonal matrix), representing systems in which correlations arise due to common input from latent units. 
        {\bf  Row 1, C}. For estimator $C_{\sf sparse}$, the covariance matrix is approximated as the inverse of a sparse matrix. This approximation describes systems in which correlations arise from a sparse set of  linear associations between the observed units. 
        {\bf  Row 1, D}.  For estimator $C_{\sf sparse+latent}$, the covariance matrix is approximated as the inverse of the sum of a sparse matrix and a low-rank matrix. This approximation describes a model wherein correlations arise due to sparse associations between the recorded cells \emph{and} with several latent units. \\
{\bf Row 2:} Examples of $50\times 50$ correlation matrices corresponding to each structure: {\bf A.} the diagonal correlation matrix, {\bf B.} a factor model with two latent units, {\bf C.}  a correlation matrix with 85\%  off-diagonal zeros in its inverse, and {\bf  D.} a correlation matrix whose inverse is the sum of a rank-1 (\ie one latent unit) matrix and a sparse matrix with 89\% off-diagonal zeros. 
\\
{\bf Row 3:} Sample correlation matrices calculated from samples of size $n=1000$ drawn from simulated random processes with respective correlation matrices shown in Row 2.  The structure of the sample correlation matrix is difficult to discern.
\\
{\bf Row 4:} Correlation matrix estimates computed by estimators with matching structure from the same data as the sample correlation matrices in Row 3. The regularized estimates are closer to the truth than the sample correlation matrices.
\\
{\bf Row 5:} Excess losses (Eq.~\ref{eq:excess-loss}) for the five estimators as a function of sample size. The error bars indicate the standard error of the mean based on 30 samples.  Estimators with structure that matches the true model converged to zero faster than the other estimators. Some exceptions occur when the sample is too small to reveal the structure in the data. In these cases estimators with simpler structures can be more efficient than estimators with true structure.
\\
{\bf Row 6:} Relative cross-validation losses (Eq.~\ref{eq:rel-cv-loss}) for the five estimators with respect to the matching estimator. Error bars indicate the standard error of the mean based on 30 samples.
    }
    \label{fig:02}
\end{FPfigure}

@@

The target of estimator $C_{\sf factor}$ is the factor model $L + \Psi$, where $L$ is the $p\times p$ positive definite matrix with low rank and $\Psi$ is the diagonal matrix of independent variances.  The estimator, 
\begin{equation}\label{eq:c-factor}
C_{\sf factor} = (1-\lambda) C_{\sf 0} + \lambda (L + \Psi),
\end{equation}
has two hyperparameters: the rank of $L$ (\ie the number of latent factors) and the shrinkage intensity $\lambda$. The structure imposed by $C_{\sf factor}$ favors conditions in which the population activity is linearly driven by a number of latent factors that affect many cells while direct interactions between the recorded cells are insignificant (\figref{02}{Row 1, B}).

Estimator $C_{\sf sparse}$ is produced by approximating the sample covariance matrix by the inverse of a sparse matrix $S$: 
\begin{equation}\label{eq:c-sparse}
C_{\sf sparse} = S^{-1}.
\end{equation}
Here $S$ is a sparse matrix, \ie one in which a large fraction of off-diagonal elements are set to zero.  The estimator has one hyperparameter that determines the sparsity (fraction of off-diagonal zeros) in $S$. The problem of finding the optimal set of non-zero elements of the precision matrix is known as \emph{covariance selection} \cite{Dempster:1972}. The structure imposed by $C_{\sf sparse}$ favors conditions in which neural correlations arise from direct linear effects (\sq{interactions}) between some pairs of neurons (\figref{02}{Row 1, C}).

@@

We refer to the sparse partial correlations in estimators $C_{\sf sparse}$ and $C_{\sf sparse+latent}$ as as \sq{interactions}.

@@

The evaluation of any covariance matrix estimator, $C$, is performed with respect to a \emph{loss function} $\loss{C,\Sigma}$ to quantify its discrepancy from truth, $\Sigma$.  The loss function must attain its minimum when $C=\Sigma$.

@@

The choice of the normal loss function is motivated by mathematical convenience. We expect that the main conclusions of our study will not change qualitatively with other well behaved loss functions, such as Stein's entropy loss or quadratic loss \cite{James:1961, Fan:2008, Ledoit:2004, Schafer:2005}.

@@

We drew 30 independent samples of sizes $n=250$, 500, 1000, 2000, and 4000 from each model and computed the excess loss for each of the five estimators.  The hyperparameters of the regularized estimators were optimized by nested cross-validation using only the data in the sample.  All the regularized estimators produced better estimates (lower excess loss) than the sample covariance matrix.  However, estimators whose structure matched the true model typically outperformed the other estimators (\figref{02}{\,row 5}).  There were two exceptions: First, for some smaller samples, the data were insufficient to reveal the true correlation structure and the estimators with simpler structures, $C_{\sf diag}$ and $C_{\sf factor}$, often outperformed the estimators with the matching structure (\figref{02}{\,Row 5, C and D}).  Second, $C_{\sf sparse+latent}$ often performed as well as $C_{\sf sparse}$ on data from models without latent units because it reliably inferred the correct number of latent units: zero.

@@

\begin{FPfigure}
\begin{center}
\includegraphics{./figures/Figure-Supp01.pdf}
\end{center}
\caption{{\bf All-to-all performance comparisons of the sample covariance matrix and the four regularized estimators with respect to multivariate normal cross-validation loss.}
\\{\bf A--D.} These panels are identical to those in \figref{04}{A--D}.
\\{\bf E.} $C_{\sf sparse}$ outperforms $C_{\sf 0}$: median improvement 0.15 nats/neuron, $p=3.9\times 10^{-5}$.
\\{\bf F.} $C_{\sf sparse}$ performs similarly to $C_{\sf diag}$: median improvement $1.0\times10^{-3}$ nats/neuron, $p=0.13$.
\\{\bf G.} $C_{\sf sparse}$ outperforms $C_{\sf factor}$: median improvement $0.15$ nats/neuron, $p=1.2\times10^{-4}$.
\\{\bf H.} $C_{\sf factor}$ outperforms $C_{\sf 0}$: median improvement $0.029$ nats/neuron, $p=2.7\times10^{-4}$.
\\{\bf I.} $C_{\sf factor}$ performs worse than $C_{\sf diag}$: median improvement $-0.16$ nats/neuron, $p=1.6\times10^{-4}$.
\\{\bf J.} $C_{\sf diag}$ outperforms $C_{\sf 0}$: median improvement $0.14$ nats/neuron, $p=2.7\times10^{-5}$.
}
\label{supp:01}
\end{FPfigure}

\begin{figure}[!ht]
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,center},capbesidewidth=8.3cm}}]{figure}[\FBwidth]
{\caption{{\bf The sparse+latent estimator outperforms the other estimators under the quadratic loss (Eq.~\ref{eq:quadratic}) just as it did under the normal loss (Eq.~\ref{eq:loss}) used in Fig.~\ref{fig:04}.}
    Histograms of the relative cross-validation loss (Eq.~\ref{eq:rel-cv-loss}) of estimators $C_{\sf 0}$, $C_{\sf diag}$, $C_{\sf factor}$, and $C_{\sf sparse}$ with respect to $C_{\sf sparse+latent}$ using the quadratic loss function.
    The histograms were obtained from 31 imaged sites in 15 mice. 
    All medians (red dashed lines) were significantly greater than zero, indicating the dominance of $C_{\sf sparse+latent}$ over the other estimators. 
    The arrow heads indicate the results for the site shown in Fig.~\ref{fig:03} and Fig.~\ref{fig:05}.
    The $p$-values are for the two-sided Wilcoxon's signed rank test.
    \\{\bf A.} $C_{\sf sparse+latent}$ outperforms $C_{\sf 0}$: median $\Delta\ell_{C_{\sf 0},C_{\sf sparse+latent}}$ = 0.35, $p=1.7\times 10^{-6}$.
    \\{\bf B.} $C_{\sf sparse+latent}$ outperforms $C_{\sf diag}$: median $\Delta\ell_{C_{\sf diag},C_{\sf sparse+latent}}$ = $2.5\times 10^{-3}$, $p=1.0\times 10^{-4}$.
    \\{\bf C.} $C_{\sf sparse+latent}$ outperforms $C_{\sf factor}$: median $\Delta\ell_{C_{\sf factor},C_{\sf sparse+latent}}$ = 0.27, $p=1.2\times 10^{-6}$.
    \\{\bf D.} $C_{\sf sparse+latent}$ outperforms $C_{\sf sparse}$: median $\Delta\ell_{C_{\sf sparse},C_{\sf sparse+latent}}$ = $3.7\times 10^{-4}$, $p=2.2\times 10^{-3}$.
}
\label{supp:02}}
{\includegraphics{./figures/Figure-Supp02.pdf}}
\end{figure}
